Distinguishing NFW and Isothermal Density Profiles with Gravitational Lensing

### 2018-04-10 paper.tex
Added link for ellipses
Now creates basic lensed images
Renamed files
Notes from meeting

\begin{abstract}
    abstract!!
\end{abstract}

@@

Ellipticity

prove that spherical density profiles only have tangential shear

@@

\subsection{Current plan}
\begin{itemize}
    \item Calculate tangential shear and deflection angle for NFW and SIS
    \item Consider single foreground lens halo with many
    \item How to arrange and distribute background halos?
    \begin{itemize}
        \item Initial ellipticity
        \item angular density on sky
        \item sizes
    \end{itemize}
    \item Apply shear and deflection angle to background galaxies
    \item Attempt to fit both profiles, subtracting intrinsic shear, see if the fit is distinguishable
    \item How many foreground halos to test?

@@

>>>>

\begin{abstract}

\end{abstract}

@@

Ellipticity
\begin{equation}
    \epsilon(R) = \frac{2 \gamma/(1 - \kappa)}{1 + (\gamma/(1 - \kappa))^2}
\end{equation}

Prove that spherical density profiles only have tangential shear and ellipticity

@@

\subsection{Current plan}
\begin{itemize}
    \item Calculate tangential shear and deflection angle for NFW and SIS
    \item Consider single foreground lens halo with many background galaxies
    \item How to arrange and distribute background halos?
    \begin{itemize}
        \item Initial ellipticity
        \item angular density on sky
        \item sizes
    \end{itemize}
    \item Apply shear and deflection angle to background galaxies
    \item Attempt to fit both profiles, subtracting intrinsic shear, see if the fit is distinguishable
    \item How many foreground halos to test?
    \item What redshift is $\rho_\mathrm{crit}$ evaluated at?

@@

N sets of e1, e2, theta1, theta2

Analyzing data:
make histogram in annulus
mean and standard deviation
use log bins for theta

50 gals/square arcminute
5 arcminutes
z_L = 0.3
z_S = 1
M_halo = 10^15 solar masses
instrinsic ellipticity from gaussian with width 0.2
